### 2024-10-10 MetadataS1/tables/table_summary_methods_and_abundance.tex
Reorganize scripts for extract species abundance

% Mon Oct  7 10:13:44 2024

@@

Common raven & Derived from the abundance estimate of glaucous gull using incidental observations & very low & Derived from moderate quality estimate of another species, but potential difference in detectability between species &  &  & 31 &  &  \\ 

>>>>

% Thu Oct 10 16:07:59 2024

@@

Common raven & Derived from the abundance estimate of glaucous gull using incidental observations & very low & Derived from moderate quality estimate of another species, but potential difference in detectability between species &  &  & 18 &  &  \\ 
